Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
Fix acronym (jonsWAp)

\Framework uses the frequency spectrum developed by Hasselmann \etal (1973) \cite{k.hasselmannMeasurementsWindwaveGrowth1973} in the Joint North Sea Observation Project (JONSWAP).
This spectrum was developed for deep sea water, and hence is in line with our deep water hypothesis.
It is expressed as follows:
\begin{equation}
	S(\omega)=\frac{\alpha g^2}{\omega^5} \exp\left(-\frac{5}{4}\left(\frac{\omega_p}{\omega}\right)^4\right)\gamma^r
\end{equation}
where:
\begin{itemize}
	\item The constant $\alpha=0.076\left(\frac{U^2}{F g}\right)^{0.22}$, $U$ being the wind speed in $m.s^{-1}$ and $F$ the fetch\footnote{The fetch is the length of the area over which the wind is acting on the water, that is to say the distance from a lee shore.} in $m$.
	\item The constant $\omega_p=22\left(\frac{g^2}{U F}\right)$.
	\item The constant $\gamma=3.3$.
	\item The exponent term $r$ is defined as follows:
	      \begin{equation}
		      r=\exp\left(-\frac{\left(\omega-\omega_p\right)^2}{2 \sigma^2 \omega_p^2}\right)
	      \end{equation}
	\item The term $\sigma$ is as follows:
	      \[
		      \sigma=\begin{cases}
			      0.07 & \omega \leq \omega_p, \\
			      0.09 & \omega>\omega_p.
		      \end{cases}
	      \]
\end{itemize}

>>>>

\Framework uses the frequency spectrum developed by Hasselmann \etal (1973) \cite{k.hasselmannMeasurementsWindwaveGrowth1973} in the Joint North Sea Wave Project (JONSWAP).
This spectrum was developed for deep sea water, and hence is in line with our deep water hypothesis.
It is expressed as follows:
\begin{equation}
	S(\omega)=\frac{\alpha g^2}{\omega^5} \exp\left(-\frac{5}{4}\left(\frac{\omega_p}{\omega}\right)^4\right)\gamma^r
\end{equation}
where:
\begin{itemize}
	\item The constant $\alpha=0.076\left(\frac{U^2}{F g}\right)^{0.22}$, $U$ being the wind speed in $m.s^{-1}$ and $F$ the fetch\footnote{The fetch is the length of the area over which the wind is acting on the water, that is to say the distance from a lee shore.} in $m$.
	\item The constant $\omega_p=22\left(\frac{g^2}{U F}\right)$.
	\item The constant $\gamma=3.3$.
	\item The exponent term $r$ is defined as follows:
	      \begin{equation}
		      r=\exp\left(-\frac{\left(\omega-\omega_p\right)^2}{2 \sigma^2 \omega_p^2}\right)
	      \end{equation}
	\item The term $\sigma$ is as follows:
	      \[
		      \sigma=\begin{cases}
			      0.07 & \omega \leq \omega_p, \\
			      0.09 & \omega>\omega_p.
		      \end{cases}
	      \]
\end{itemize}
